---
title: "Purrr Questions w/Answers"
author: "Ben Wagner"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(purrr)
```



```{r}
mtcars
```

Question 1: Create two lists of random vectors and use map2 to get the power of the first list to the second list, by defining a function that is passed in as an argument in the mapping. 

Answer:
```{r}
x <- c(2, 4, 5, 6)
y <- c(2, 3, 4, 5)
Power <- function(x, y){
  return(x**y)
}
map2(x, y, to_Power)
```


Question 2: In the mtcars dataset, are there any cars that have a quarter mile time(qsec) faster than 20 seconds? (Hint: you may need to flatten list(mtcars$qsec)). If so, create a list of those quarter mile times.

Answer:
```{r}
Quarter_mile_times <- list(mtcars$qsec)
Quarter_mile_times <- flatten_dbl(Quarter_mile_times)
some(Quarter_mile_times, function(x) x>20)
keep(Quarter_mile_times, function(x) x>20)
```

Question 3: Using the mtcars dataset, create a list of car names (Hint: use rownames() to pull the names since there is no variable for the names). Also create a list containing the transmission types for each car. For both lists you will need to flatten. From there, return the index of the first automatic car((0 = automatic, 1 = manual), and pluck that cars name from your list.
Answer:
```{r}
names<- list(rownames(mtcars))
transmission <- list(mtcars$am)
names<- flatten_chr(names)
detect_index(flatten_dbl(transmission), function(x) x==0)
pluck(names, detect_index(flatten_dbl(transmission), function(x) x==0))

```



