---
title: "Purrr Presentation"
author: "Ben Wagner & Tshering Wangchuk"
date: "10/31/2021"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(purrr)
```

## Introduction

The Purr package belongs to the tidyverse family fundamentally used for iteration. In comparison to dplyr which mainly uses data frames, the Purr mainly works with data in a list format. The components of lists usually include:

* A *vector* - Logical, Character, Double or Integer.

* A *data frame* - storing many vectors of the same length but possibly of different types together in a single object.

* A *list* - is a way of storing many objects of any type (e.g. data frames, plots, vectors) together in a single object.


## Mapping with purrr

A *map function* applies the same action to every element of the input (such as list, vector) to the object, hence disregarding the need for for-loop functions

The map functions transform the inputs of a set of elements / vectors within a list and return an object which is the same length as the input. Map functions can be categorized by the number of lists that is being passed into the function whereby the *output* of syntax is given as *map_...* for one list, *map2_...* for two lists, *pmap_...* for multiple lists and *imap_...* for a combination of lists and indexes.

The transformation / output for these different functions regardless of the number of lists will always be delivered in the formats below:

*map() is the main mapping function and always returns a list.

*map_lgl(), map_int(), map_dbl() and map_chr() return an atomic vector, depending on the argument in the function.

*map_dfr() and map_dfc() returns a data frame. 

### Working with 1 list 

Here, we create a list of three vectors that are in double format in order to find the mean of the elements. Since the vectors in dbl format, we apply the map_dbl function and pass on the argument to find the mean, which will also be returned as a double element. 

```{r}
List_1 <- list(
  c(2.0, 2.98, 6.43),
  c(3.5, 6.0, 7))

map_dbl(List_1, mean)
map_dbl(List_1, median)
```

Using the same list above, we can also use mapping to determine other results based on the argument that is being passed into the function, where you can create customized functions. 

```{r}
List_1 %>% map(~ . * 2)
```
 
We can also use the mapping functions to pass other arguments such as logical arguments. Below, we test to see if the vectors in the list are numeric, which is the case. Utilizing the logical mapping function denoted by map_lgl(), our output returns TRUE as an object. Similarly, for map_chr(), the output is returned in character format and for integer, takes the value of 1 = True while 0 = False.  

```{r}
List_1 %>% map_lgl(is.numeric)
List_1 %>% map_chr(is.character)
List_1 %>% map_int(is.character)
```

### Working with more than one list

To demonstrate how mapping works with more than one list, we take two different lists with a set of vectors. Using the same concept as with one list, we are able to pass arguments into the functions. 

```{r}
x <- list(5, 15, 10, 30, 35, 45, 50, 60, 80, 20)
  
y <- list(10, 20, 30, 55, 25, 10, 15, 60, 70, 20)

map2_dbl(x, y, ~.x + .y)
```


### Mapping to solve realistic problems with models

The example below applies the purrr package to solve a realistic problem whereby we split a data frame into pieces, fit a model to each piece, computing the summary, then obtaining the R2.

```{r}
mtcars %>%
  split(.$cyl) %>%
  map(~ lm(mpg ~ wt, data = .)) %>%
  map(summary) %>%
  map_dbl("r.squared")
```


## Working With Lists

Since the product of most *map()* functions are lists, it is important to understand how to manipulate such objects using purrr. Within the package, there are multiple list specific functions which perform actions such as; filtering, summarizing, transforming, reshaping and combining. 

### Filtering

```{r}
Students <- list("Ben", "Tshering", "Anna", "Mary", "Chris", "Joe", "Nicole", "Marisa", "Nick", "Harry")

Test_Scores <- list(90, 100, 83, 45, 67, 78, 55, 36, 75, 92)
```


*Pluck()*:
The pluck function takes a list and an index (withing the bounds of the list) and returns the element at that index. If the index passed is not a valid index, the function returns NULL.
```{r}
pluck(Students, 6)
```
*Keep()*:
The keep function takes a list and a logical test which must be passed by the elements of the list in order for them to be included in the product. If we wanted to see all the test scores which passed the test you would write:  
```{r}
keep(Test_Scores, function(x) x>=65)
```
Conversely, the function discard() uses the same syntax as keep, but deletes the elements of the list that return TRUE for the logical test.

*Compact()*:
If your list contains NULL variables, the compact function returns the list passed to it without those NULL observations. It is important to not comfuse NULL and NA observations because the function does not deal with NA's.
```{r}
compact_list <- list(4, 5, 6, 7, 8, NULL, 10, NULL, 12)
compact(compact_list)
```
*Head_while()*:
This function, similar to keep/discard takes a list and a logical test. However, this function returns a list of all the elements that pass the test, checking each index in order until it reaches one that fails.
```{r}
head_list <- list("Happy", "Sad", "Scared", 6, 5, "Excited")
head_while(head_list, is_character)
```
### Summarizing

*Every()*, *Some()*, *Has_element()*:
These two functions are very similar, but only slightly differ for what they look for in the list. The function *every()* returns TRUE only if each element in the list passes the logical test that is passed when defining the function. The function *some()* returns true as long as 1 or more of the elements of the list pass the logical test defined. Has_element also returns a TRUE or FALSE statement, but the user passes a specific value they are searching for in the list.
```{r}
every(head_list, is.numeric)
```
```{r}
some(head_list, is.numeric)
```
```{r}
has_element(head_list, 7)
```


*Detect()*, *Detect_index()*:
Detect is similar to *every()* and *some()* for what is passed to the functions, however instead of returning TRUE of FALSE, it returns the first element that passes the logical test. *Detect_index()* returns the first index that passes the test.
```{r}
detect(head_list, is.numeric)
detect_index(head_list, is.numeric)
```

### Reshaping Lists

Reshaping lists is a very important aspect of purrr to understand because it is quite useful in the data wrangling process.

*Flatten()*:
Flatten removes the level of hierarchy from the list of lists. Flatten: _lgl(), _int(), _dbl(), _chr() all return a list of their specific types. 
In our example, we include *rerun(n, function)* which repeats a function n times which are both defined in the function.
```{r}
x <- rerun(4, sample(6))
x
```
```{r}
flatten_int(x)
```
*Transpose()*:
Transpose returns a list of pairs which is converted from a pair of lists.
```{r}
a <- rerun(2, x = runif(2), y = runif(3))
a
```
```{r}
a %>% transpose() %>% str()
```

### Joining Lists

You can join lists in two different ways. You can add a list to the end of another list or add the list to the beginning of the other.

*Append()*:
This function adds the second list passed in the definition to the end of the first. We use flatten_dbl here to show the appended list as 1. 
```{r}
list1 <- list(22, 11, 44, 55)
list2 <- list(11, 99, 77)
flatten_dbl(append(list1, list2))
```

*Prepend()*:
The function does the same as *append()*, however it adds the second list passed to the beginning of the first
```{r}
flatten_dbl(prepend(list1, list2))
```

*Cross_df()*:This function returns a data frame where each row is a combination of list elements.
```{r}
df <- list( Scores = Test_Scores,
            name = Students,
            grade = c(4, 10, 6, 8))
df

```
```{r}
cross_df(df)
```






















