---
title: "Purrr Questions"
author: "Ben Wagner & Tshering Wangchuk"
date: "10/31/2021"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(purrr)
```

```{r}
mtcars
```
Question 1: Question 1: Create two lists of random vectors of the same length and use map2 to get the power of the first list to the second list, by defining a function that is passed in as an argument in the mapping. 

```{r}

```


Question 2: In the mtcars dataset, are there any cars that have a quarter mile time(qsec) faster than 20 seconds? (Hint: you may need to flatten list(mtcars$qsec)). If so, create a list of those quarter mile times.

```{r}

```

Question 3: Using the mtcars dataset, create a list of car names (Hint: use rownames() to pull the names since there is no variable for the names). Also create a list containing the transmission types for each car. For both lists you will need to flatten. From there, return the index of the first automatic car((0 = automatic, 1 = manual), and pluck that cars name from your list.

```{r}

```



